The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Put symbols and parameters in different tables with a nice layout
Cluster hypotheses as far as this follows naturally

We expect
% Hypothesis: general
\item We hypothesize that the error made today, using BD tree priors,
increases with an increased number or stronger effect of multiple birth events.
This is straightforward: without multiple birth events or such event having
no effect, the MBD model falls back to a BD model. We expect larger
errors when we deviate more from the BD model's assumptions. 
Additionally, we hypothesize MBD having a stronger effect if the normal
speciation process is less pronounced. The more speciations are caused by the
BD process, there are relatively less multiple-birth events.
To put this hypothesis, H1, into an explicit equation, 
we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

\begin{equation}
<e> = f(s)
\end{equation}

Where $<e>$ denotes the expected error, $f$ is a monotonously increasing 
function of unknown shape, $n_{taxa}^{MBD}$ is the number of taxa created
in multiple-birth events and $n_{taxa}^{BD}$ is the number of taxa created
by the standard BD specition process.

@@

\item We have the hypothesis, H7, 
that there is no difference in inference errors if the MBD process
generates many species in many modest MB events or few intense MB events.

@@

\item We have the hypothesis, H2, 
that the effect of extinction rates is neutral, 
as extinctions will hit lineages created by both speciation processes equally.

@@

\item Due to the proportionality of the term within $f$, 
we have the hypothesis, H3, 
that the timing of a multiple birth event (be it close to the
crown age or close to the present) to have no effect. Compared to a late
multiple birth event, an early multiple birth event may have a 
longer-lasting effect (as the next speciation event will be later), but it
will create less new species, as there are still fewer taxa.

@@

@@

\item We start simulating $N_{S} = 1000$ MBD trees,
with either 50, 100 and 200 taxa.
We have the hypothesis H5, that the number of taxa does not
have an effect on the error being made, as there is no
diversity dependency in any of the processes.
We have the hypothesis H6, that for a higher number of taxa 
the variance in the error decreases, as more information is present
in the simulated phylogenies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description\\
    \hline
    \hline
    $n_{\mathbb{M}}$      & Number of extinct and extant taxa created by a multiple-birth event \\
    $n_{\mathbb{B}}$      & Number of extinct and extant taxa created by a single-birth event \\
    $s$                   & Extent/strength of the multiple birth process \\
    $L_c$                 & MCMC chain length \\
    $L_{sc}$              & MCMC sub-chain length \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:symbols}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We have the hypothesis $\mathcal{H}_1$ that, for a higher $s$, 
the inference error $e$ will increase:

\begin{equation}
e = f(s)
\end{equation}

Where $f$ is a monotonously increasing function of unknown shape.

@@

The MBD process has multiple components, that may cause 
different values of $e$ for identical values of $s$.

One MBD component that may cause 
different values of $e$ for identical values of $s$
is the MBD regime: which can be many modest 
multiple-speciation events, or few intense ones. 
As we have no prior expectations, we have the (null) hypothesis, 
$\mathcal{H}_7$, that the MBD regime has no effect on $e$.

@@

Another MBD component that may cause 
different values of $e$ for identical values of $s$
is the effect of extinction. 
As extinctions will hit lineages created by both speciation processes equally,
and we have no additionaly prior expectations,
we have the (null) hypothesis, 
$\mathcal{H}_2$, that extinction has no effect on $e$.

@@

Another MBD component that may cause 
different values of $e$ for identical values of $s$,
is the timing of a multiple-birth event: be it close to the
crown age or close to the present. 
Compared to a late multiple birth event, an early multiple birth event may have a 
longer-lasting effect (as the next speciation event will be later), but it
will create less new species, as there are still fewer taxa.
As we have no prior expectations,
we have the (null) hypothesis, 
$\mathcal{H}_3$, that the timing of multiple-birth events has no effect on $e$.

@@

Another MBD component that may cause 
different values of $e$ for identical values of $s$,
is the number of taxa in a phylogeny,
As there is no diversity dependency in any of the processes
and we have no further prior expectations, we have
the (null) hypothesis $\mathcal{H}_5$, that the number of
taxa has no effect on $e$.
As a higher number of taxa increases the information content in a
phylogeny, we have hypothesis $\mathcal{H}_6$ that the
variance in $e$ decreases.

@@

\item We start simulating $N_{S} = 1000$ MBD trees,
with either 50, 100 and 200 taxa.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Description\\
    \hline
    \hline
    $e$                   & Inference error \\
    $n_{\mathbb{M}}$      & Number of extinct and extant taxa created by a multiple-birth event \\
    $n_{\mathbb{B}}$      & Number of extinct and extant taxa created by a single-birth event \\
    $s$                   & Extent/strength of the multiple birth process \\
    $L_c$                 & MCMC chain length \\
    $L_{sc}$              & MCMC sub-chain length \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:symbols}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
